Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-03 popl24/intro.tex
checkpoint

In \ref{section-minicat} we develop a new probabilistic programming
language $\minifed$ for defining synchronous distributed protocols
over the binary field. The syntax and semantics provides a succinct
account of \emph{views} and (synchronous) messaging between protocol
\emph{clients}. In this Section we consider small example protocols
including oblivious transfer, communications encryption with one-time
pads, and additive secret sharing. In Section \ref{section-pmf} we
formulate \emph{program distributions}, a formalism for expressing
dependencies between secrets and views, useful for expressing
intensional characteristics of protocols and precisely quantifying
allowable information leakage in terms of protocol outputs. On this
basis we then formulate a novel hyperproperty of program execution
traces, called \emph{noninterference modulo output ($\NIMO$)} that we
demonstrate implies passive simulator security. In Section
\ref{section-bruteforce} we define a brute force mechanism for
verifying passive security in $\minifed$ protocols, that is also
amenable to HPC optimizations via translation of $\minifed$ protocols
into Datalog \cnote{I think this Section can be on the chopping block
  for space savings, since it's based on truth table
  computation/Datalog semantics.}. In Section \ref{section-metalang}
we define a new metaprogramming language $\metaprot$ that dynamically
generates $\minifed$ protocols. It includes control and data
structures and is able to express logical protocol components, and
enjoys a type safety result that guarantees that generated protocols
are semantically well-defined. Our key analysis results are presented
in Section \ref{section-composition}, where we show how intensional,
automatically certifiable properties of program components can be
composed to obtain whole-program MPC security. We consider the GMW and
YGC protocols as examplars, both of which use \emph{circuit}
abstractions comprising \emph{gates} in arbitrarily large
configurations, and show how gates can be automatically certified to
ensure security in circuits that use them in a manner that scales to
any circuit size. This approach is extensible, in that new gate
implementations can be automatically certified to guarantee safe
inclusion in circuit libraries.

>>>>

In \ref{section-minicat} we develop a new probabilistic programming
language $\minifed$ for defining synchronous distributed protocols
over the binary field. The syntax and semantics provides a succinct
account of \emph{views} and (synchronous) messaging between protocol
\emph{clients}. In this Section we consider small example protocols
including oblivious transfer, communications encryption with one-time
pads, and additive secret sharing. In Section \ref{section-pmf} we
formulate \emph{program distributions}, a formalism for expressing
dependencies between secrets and views, useful for expressing
intensional characteristics of protocols and precisely quantifying
allowable information leakage in terms of protocol outputs. On this
basis we then formulate a novel hyperproperty of program execution
traces, called \emph{noninterference modulo output ($\NIMO$)} that we
demonstrate implies passive simulator security. In Section
\ref{section-bruteforce} we define a brute force mechanism for
verifying passive security in $\minifed$ protocols, that is also
amenable to HPC optimizations via translation of $\minifed$ protocols
into Datalog \cnote{I think this Section can be on the chopping block
  for space savings, since it's based on truth table
  computation/Datalog semantics.}.

In Section \ref{section-metalang} we define a new metaprogramming
language $\metaprot$ that dynamically generates $\minifed$
protocols. It includes control and data structures and is able to
express logical protocol components, and enjoys a type safety result
that guarantees that generated protocols are semantically
well-defined. Our key analysis results are presented in Section
\ref{section-composition}, where we show how intensional,
automatically certifiable properties of program components can be
composed to obtain whole-program MPC security. We consider the GMW and
YGC protocols as examplars, both of which use \emph{circuit}
abstractions comprising \emph{gates} in arbitrarily large
configurations, and show how gates can be automatically certified to
ensure security in circuits that use them in a manner that scales to
any circuit size. This approach is extensible, in that new gate
implementations can be automatically certified to guarantee safe
inclusion in circuit libraries.
